---
title: "ExploratoryAnalysis1"
author: "LRA"
date: "12/17/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```

## June in situ productivity and prevelance

```{r shoot level}
growth <- read.csv("InSituGrowthData.csv")
growth <- na.omit(growth)
growth$Prev <- as.factor(growth$Prev)
cdplot(Prev~mm2.sh.d,data=growth,xlab = "Growth (mm per shoot per day)",ylab="Prevelance")
```

At the shoot level, there's a slightly higher probability (~0.4) that the leaves will be infected for slower-growing shoots,
while faster growing shoots have a slightly lower probability of infection (~0.2)

```{r leaf level}
leaf <- read.csv("LeafGrowth.csv")
leaf$Prev <- as.factor(leaf$Prev)
cdplot(Prev~mm2.l.d,data=leaf,xlab = "Growth (mm per leaf per day)",ylab="Prevelance")
```

At the leaf level, faster growing leaves are much less likely to be infected. This result is because the youngest leaves
are the fastest growing and least likely to be infected.

```{r biomass}
plot(Old.g~mm2.sh.d,data=growth,xlab="Growth (mm per shoot per day)",ylab="Starting biomass (g)")
```

Unsurprisingly, bigger shoots have higher growth rates